MCDA-EVSE

### 2024-05-24 code/MCDA-EVSE.Rmd
add neighborhood

  mutate(score = 
  0.12*scl_density + 
  0.18*scl_evse_re +
  0.15*scl_elec + 
  0.1*scl_drivingpop +
  0.1*scl_parking_re + 
  0.05*scl_policefire_re + 
  0.05*zone_score + 
  0.12*scl_acc_re +
  0.13*scl_elect_use)

@@

rank_toplot <- fishnet_nowater %>% 
  left_join(rank_compare, by = "uniqueID")
ggplot()+
  geom_sf(data=fishnet, color="black", fill="white") +
  geom_sf(data=rank_toplot, color="black", aes(fill=avg_rank))
```

>>>>

@@

rank_toplot <- fishnet_nowater %>% 
  left_join(rank_compare, by = "uniqueID")
ggplot()+
  geom_sf(data=fishnet, color="black", fill="white") +
  geom_sf(data=rank_toplot, color="black", aes(fill=avg_rank)) +
  geom_sf(data=acme, color="red")
```

# Public Private Partnership

acme <- read.csv(here("data", "raw", "acme.csv")) %>% 
  st_as_sf(., coords = c("Longitude", "Latitude"), crs = 4326) %>% 
  mutate(longitude= unlist(map(geometry, 1)),
         latitude = unlist(map(geometry, 2)))

final <- fishnet_nowater %>% 
  left_join(., rank_compare, by = "uniqueID")

pal <- colorBin(palette = "viridis", # change the color palette here
                domain = final$avg_rank, # change the parameter name after $
                bins = c(200, 400, 600, 800, 1000, 1200)) # change the bins here

labs <- paste0("<strong>", tst$NAME,
               "</strong><br/>EVSE Suitability: ", tst$score, 
               "</strong><br/>Population Density (sqkm): ", tst$density,
               "</strong><br/>Accessibility Score: ", tst$TSFCA,
               "</strong><br/>Driving Population %: ", tst$driving_pop,
               "</strong><br/> Registered EV: ", tst$elec_cnt,
               "</strong><br/>Avg Distance to EVSE: ", tst$evse.nn,
               "</strong><br/>Avg Distance to Parking: ", tst$parking.nn,
               "</strong><br/>Avg Distance to Police & Fire: ", tst$evse.nn
               )

labs_acme <- paste0("</strong><br/>ACME Address ", acme$Address)

```{r}
leaflet <- final %>%
  st_transform("EPSG:4326") %>% 
  leaflet() %>%
  setView(lng = -75.1652, lat = 40.0126, zoom = 10.5) %>%
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addPolygons(weight = 1,
              fillColor = ~pal(avg_rank), # change the name of the parameter in the bracket
              fillOpacity = 1) %>%
  addCircleMarkers(
    data = acme,  # Replace with your actual point data
    lng = ~longitude,  # Replace with the appropriate variable in your point dataset for longitude
    lat = ~latitude,  # Replace with the appropriate variable in your point dataset for latitude
    weight = 0.5,
    radius = 4,
    fillColor = "red",  # Set the fill color for the markers
    fillOpacity = 1,
    popup = ~labs_acme  # Replace with the appropriate variable in your point dataset for popup text
  ) %>% 
  addLegend(position = "bottomright",
            pal = pal,
            values = ~avg_rank, # change the name of the parameter after ~
            title = "EVSE Suitability Score") # change the name of the legend

leaflet
```
